Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-05-25 ms.tex
adjusted the quickk inclination calculations.

\begin{deluxetable*}{lllcccccccl}
\tablecaption{Brown Dwarf Properties}\label{tab:bdProp}
\tablewidth{0pt}
\tablehead{
 & \multicolumn{2}{c}{Spectral Type} \\
\colhead{Name} & 
\colhead{Opt} & 
\colhead{NIR} & 
\colhead{$d$} & 
\colhead{2MASS $H$} & 
\colhead{$J-K_s$} & 
\colhead{\teff} & 
\colhead{P$_{rot}$} &
\colhead{$v\sin{i}$} & 
\colhead{$i$\tablenotemark{a}} & 
\colhead{Refs} \\
 &  &  & \colhead{(pc)} & &  & \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($\degr$)} \\
 }
\startdata
\sha\ & L5 & L7 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
\shb\ & L4.5p & L5 & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1614$\pm$100\tablenotemark{c} & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 83 & 5-10 \\
\enddata
\tablenotetext{a}{Estimated inclination angle $i$ assuming a radius = 1 Jupiter radius, so that $\sin{i}$ = 8.2$\times$10$^{-3}Pv\sin{i}$, where $P$ is in hours and $v\sin{i}$ is in km/s. A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on. \textcolor{red}{\bf I get 8.0$\times 10^{-3} Pv\sin(i)$.}}
\tablenotetext{b}{Tentative period.}
\tablenotetext{c}{Estimated from the \citet{2015ApJ...810..158F} {\teff}/spectral type relation.}
\tablerefs{(1) \citet{2003AJ....126.2421C};
(2) \citet{2012ApJ...752...56F}; 
(3) \citet{2015ApJ...810..158F};
(4) \citet{2004MNRAS.354..378K};
(5) \citet{2010ApJ...723..684B};
(6) \citet{2008ApJ...686..528L}; 
(7) \citet{2016MNRAS.455..357S};
(8) \citet{2015ApJ...798...73G};
(9) \citet{2015ApJ...799..154M}
(10) \citet{2015ApJ...798L..13Y}; 
}
\end{deluxetable*}

>>>>

\begin{deluxetable*}{lllcccccccl}
\tablecaption{Brown Dwarf Properties}\label{tab:bdProp}
\tablewidth{0pt}
\tablehead{
 & \multicolumn{2}{c}{Spectral Type} \\
\colhead{Name} & 
\colhead{Opt} & 
\colhead{NIR} & 
\colhead{$d$} & 
\colhead{2MASS $H$} & 
\colhead{$J-K_s$} & 
\colhead{\teff} & 
\colhead{P$_{rot}$} &
\colhead{$v\sin{i}$} & 
\colhead{$i$\tablenotemark{a}} & 
\colhead{Refs} \\
 &  &  & \colhead{(pc)} & &  & \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($\degr$)} \\
 }
\startdata
\sha\ & L5 & L7 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 17-26 & 1-5 \\
\shb\ & L4.5p & L5 & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1614$\pm$100\tablenotemark{c} & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 54-90 & 5-10 \\
\enddata
\tablenotetext{a}{Estimated inclination angle $i$, so that $\sin{i}$ = 8.0$\times$10$^{-3}Pv\sin{i} / R$, where $P$ is in hours and $v\sin{i}$ is in km/s and $R$ is assumed to be 0.8 to 1.2 $\times$ the equatorial radius of Jupiter. A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on.}
\tablenotetext{b}{Tentative period.}
\tablenotetext{c}{Estimated from the \citet{2015ApJ...810..158F} {\teff}/spectral type relation.}
\tablerefs{(1) \citet{2003AJ....126.2421C};
(2) \citet{2012ApJ...752...56F}; 
(3) \citet{2015ApJ...810..158F};
(4) \citet{2004MNRAS.354..378K};
(5) \citet{2010ApJ...723..684B};
(6) \citet{2008ApJ...686..528L}; 
(7) \citet{2016MNRAS.455..357S};
(8) \citet{2015ApJ...798...73G};
(9) \citet{2015ApJ...799..154M}
(10) \citet{2015ApJ...798L..13Y}; 
}
\end{deluxetable*}
